\item
    \textit{N White, }\textbf{R Parsons}\textit{, D Borg, G Collins, A Barnett}\textbf{\hfill{J Clin Epi (2024)}}\par
    \textit{Planned but ever published? A retrospective analysis of clinical prediction model studies registered on clinicaltrials.gov since 2000.}
\item
	\textit{L De Assis, L Harder, J Lacerda, }\textbf{R Parsons}\textit{, M Kaehler, I Cascorbi, I Nagel,}\textbf{\hfill{Sci Rep (2024)}}\par
	\textit{O Rawashdeh, J Mittag, H Oster}\par
    \textit{Tuning of liver circadian transcriptome rhythms by thyroid hormone state in male mice.}
\item
    \textit{N White, }\textbf{R Parsons}\textit{, G Collins, A Barnett}\textbf{\hfill{BMC Med (2023)}}\par
    \textit{Evidence of questionable research practices in clinical prediction models.}
\item
    \textit{B Abell, S Naicker, D Rodwell, T Donovan, A Tariq, M Baysari, }\textbf{R Parsons}\textit{,}\textbf{\hfill{Implement Sci (2023)}}\par\
	\textit{R Blythe, SM McPhail}\par
    \textit{Identifying barriers and facilitators to successful implementation of computerized clinical decision support systems in hospitals: a NASSS framework-informed scoping review.}
\item
    \textit{RD Blythe, }\textbf{R Parsons}\textit{, AG Barnett, SM McPhail, NM White}\textbf{\hfill{J Clin Epi (2023)}}\par
    \textit{Vital signs-based deterioration prediction model assumptions can lead to losses in prediction performance.}
\item
    \textbf{R Parsons}\textit{, RD Blythe, AG Barnett, SM Cramb, SM McPhail}\textbf{\hfill{JOSS (2023)}}\par
    \textit{predictNMB: An R package to estimate if or when a clinical prediction model is worthwhile.}
\item
    \textbf{R Parsons}\textit{, RD Blythe, SM Cramb, SM McPhail}\textbf{\hfill{JAMIA (2023)}}\par
    \textit{Integrating economic considerations into cutpoint selection may help align clinical decision support towards value-based healthcare.}
\item
    \textit{O Durunna, JA Carroll, JW Dailey, D Damiran, KA Larson, E Timsit, }\textbf{R Parsons}\textit{,}\textbf{\hfill{Front Genet (2023)}}\par
	\textit{G Manafiazar, HA Lardner}\par
    \textit{Phenotypic and genetic parameters of circadian rhythms from core body temperature profiles and their relationships with beef steers’ production efficiency profiles during successive winter feeding periods.}
\item
    \textit{J-F Harmsen, M van Weeghel, }\textbf{R Parsons}\textit{, GE Janssens, J Wefers, D van Moorsel,}\textbf{\hfill{Cell Rep (2022)}}\par
	\textit{J Hansen, J Hoeks, MKC Hesselink, RH Houtkooper, P Schrauwen}\par
    \textit{Divergent remodeling of the skeletal muscle metabolome over 24h between young, healthy men and older, metabolically compromised men.}
\item
    \textit{S Cramb, A Rolley, CR Gibbs, }\textbf{R Parsons}\textit{, C Hayden, A Woodley, }\textbf{\hfill{QUT ePrints (2022)}}\par
	\textit{K Vallmuur, J Warren}\par
	\textit{Injury Treatment and Rehabilitation Accessibility Queensland Index (iTRAQI) Pilot for Moderate-to-Severe Traumatic Brain Injury: Technical report.}
\item
    \textbf{R Parsons}\textit{, RD Blythe, SM Cramb, SM McPhail}\textbf{\hfill Gerontology (2022)}\par
	\textit{Inpatient Fall Prediction Models: A Scoping Review.}
\item
	\textit{R Blythe, }\textbf{Parsons R}\textit{, NM White, D Cook, SM McPhail}\textbf{\hfill{BMJ Qual Saf (2022)}}\par
	\textit{A scoping review of real-time automated clinical deterioration alerts and evidence of impacts on hospitalised patient outcomes.}
\item
	\textit{LVM de Assis, L Harder, JT Lacerda, }\textbf{R Parsons}\textit{, M Kaehler, I Cascorbi, I Nagel, }\textbf{\hfill eLife (2022)}\par
	\textit{O Rawashdeh, J Mittag, H Oster}\par
    \textit{Rewiring of liver diurnal transcriptome rhythms by triiodothyronine (T3) supplementation.}
\item
    \textbf{R Parsons}\textit{, SM Cramb, SM McPhail}\textbf{\hfill BMJ Open (2021)}\par 
    \textit{Clinical prediction models for hospital falls: a scoping review protocol.}
\item
    \textit{Bassi GL, JY Suen, N White, HJ Dalton, J Fanning, A Corley, S Shrapnel,}\textbf{\hfill Crit Care Explor (2021)}\par
	\textit{S Hinton, S Forsyth, }\textbf{R Parsons}\textit{, JG Laffey, E Fan, R Bartlett, D Brodie, A Burrell, D Chiumello, A Elhazmi, G Grasselli, C Hodgson, S Ichiba, C Luna, E Marwali, L Merson, S Murthy, A Nichol, M Panigada, P Pelosi, A Torres, PY Ng, M Ogino, Fraser JF}\par
    \textit{Assessment of 28-Day In-Hospital Mortality in Mechanically Ventilated Patients With Coronavirus Disease 2019: An International Cohort Study.}
\item
    \textit{GH Goh, PJ Mark, D Blache, D Binks, }\textbf{R Parsons}\textit{, O Rawashdeh, SK Maloney}\textbf{\hfill J Therm Biol (2021)}\par 
    \textit{Diet-altered body temperature rhythms are associated with altered rhythms of clock gene expression in peripheral tissues in vivo.}
\item
    \textbf{R Parsons}\textit{, R Parsons, N Garner, H Oster, O Rawashdeh}\textbf{\hfill Bioinformatics (2020)}\par 
    \textit{CircaCompare: a method to estimate and statistically support differences in mesor, amplitude and phase, between circadian rhythms.}
\item
    \textbf{R Parsons}\textit{, K Newbigin, D Deller, R Edwards, R McBean}\textbf{\hfill Respirology (2019)}\par 
    \textit{Stonemasons with silicosis: Preliminary findings and a warning message from Australia.}
\item
    \textit{C Haran, R McBean, }\textbf{R Parsons}\textit{, D Wong}\textbf{\hfill J Med Imaging Radiat Oncol (2019)}\par 
    \textit{Five-year trends of bone scan and prostate-specific membrane antigen positron emission tomography utilization in prostate cancer: A retrospective review in a private centre.}
\item
    \textit{R McBean, B O'Kane, }\textbf{R Parsons}\textit{, D Wong}\textbf{\hfill J Med Imaging Radiat Oncol (2019)}\par 
    \textit{Lu177‐PSMA therapy for men with advanced prostate cancer: Initial 18 months experience at a single Australian tertiary institution.}
\item
    \textbf{Wesley Dust Disease Research Centre.}\textbf{\hfill ACARP (2019)}\par 
    \textit{A Clinical, Radiological and Occupational Review of Coal Mine Dust Lung Disease in Queensland.}
\item
    \textit{O Rawashdeh, }\textbf{R Parsons}\textit{, E Maronde}\textbf{\hfill Neural Plast (2018)}\par 
    \textit{Clocking in time to gate memory processes: The circadian clock is part of the ins and outs of memory.}
